Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-01-30 automatica/paper.tex
added forward reference to safety theorem

We use finite-precision arithmetic to model the plant. 
This is an approximation that speeds up each CEGIS iteration, 
however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.  
In this stage, we represent the plant using double-precision floating-point numbers 
and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
We employ a compositional numerical library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
We check that the controller is safe starting from each vertex of the set of initial states,  
and show that this is sufficient to prove safety from any state in this set. \note{add forward reference to proof.}

@@

\begin{theorem} 
If a controller is safe for each of the corner cases of our hypercube of
allowed initial states, i.e., the vertex states, it is safe for any initial state in the hypercube. 
\end{theorem}
\begin{proof}
Consider the set of initial states, $X_0$, which we assume to be convex since it is a hypercube. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
%
where $x_k^i$ denotes the trajectories obtained from the single vertex
$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
convex set, by those generated from the vertices. 
\qed
\end{proof}
In conclusion, we only need to check $2^n$ initial states, 
where $n$ is the dimension of the state space (number of continuous variables).

>>>>

We use finite-precision arithmetic to model the plant. 
This is an approximation that speeds up each CEGIS iteration, 
however it necessitates a further stage where we verify that the errors introduced by the approximation have not resulted in a controller that is unsafe when executed on a plant expressed over real numbers.  
In this stage, we represent the plant using double-precision floating-point numbers 
and we use the Boost interval arithmetic library~\cite{DBLP:journals/tcs/BronnimannMP06} to bound the error in this representation. 
We employ a compositional numerical library to model the fixed point arithmetic for the controller~\cite{CNL} within double-precision floating-point numbers. 
We check that the controller is safe starting from each vertex of the set of initial states,  
and show that this is sufficient to prove safety from any state in this set (see Theorem~\ref{th:safety}). %\note{add forward reference to proof.}

@@

\begin{theorem}
  \label{th:safety}
If a controller is safe for each of the corner cases of our hypercube of
allowed initial states, i.e., the vertex states, it is safe for any initial state in the hypercube. 
\end{theorem}
\begin{proof}
Consider the set of initial states, $X_0$, which we assume to be convex since it is a hypercube. 
Name $v_i$ its vertices, where $i=1,\ldots, 2^n$.  
Thus any point $x \in X_0$ can be expressed by convexity as $x = \sum_{i=1}^{2^n} \alpha_i v_i$, 
where $\sum_{i=1}^{2^n} \alpha_i =1$. Then if $x_0=x$, we obtain 
\begin{align*}
x_k   &= (A_d - B_d K)^k x = (A_d - B_d K)^k \sum_{i=1}^{2^n} \alpha_i v_i \\
      &= \sum_{i=1}^{2^n} \alpha_i (A_d - B_d K)^k v_i = \sum_{i=1}^{2^n} \alpha_i x_k^i, 
 \end{align*}     
%
where $x_k^i$ denotes the trajectories obtained from the single vertex
$v_i$.  We~conclude that any $k$-step trajectory is encompassed, within a
convex set, by those generated from the vertices. 
\qed
\end{proof}
In conclusion, we only need to check $2^n$ initial states, 
where $n$ is the dimension of the state space (number of continuous variables).
